Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
cleaning up numerical experiments

  \pause
  Domain Overlap Studies for the Parallel Neumann-Ulam Method
  \begin{itemize}
  \item Correlate domain overlap behavior to linear system properties
  \item Analyze random walk transport with respect to the operator:
    \begin{itemize}
    \item Eigenvalues
    \item Sparsity
    \item Asymmetry
    \end{itemize}
  \item Evaluate communication cost
  \item Evaluate memory cost
  \end{itemize}

  \pause
  Domain Replication Studies for the Parallel Neumann-Ulam Method
  \begin{itemize}
  \item Feasibility from a memory perspective
  \item Impact on scalability
  \item Impact on load balancing
  \end{itemize}

@@

  Parallel Performance and Numerical Accuracy Studies for the MCSA
  Method
  \begin{itemize}
  \item Characterize Neumann-Ulam parameters required for good
    correction
  \item Feasibility of MCSA with full-clip Neumann-Ulam
  \item Performance for asymmetric systems
  \item Memory usage compared to Krylov methods
  \end{itemize}

  \pause
  Parallel Performance and Numerical Accuracy Studies for the FANM
  Method
  \begin{itemize}
  \item Feasibility for problems of interest
  \item Memory usage vs. Newton-Krylov methods
  \item Scalability vs. Newton-Krylov methods
  \end{itemize}

>>>>

  \pause
  \textbf{Domain Overlap Studies for Parallel Neumann-Ulam Method} 
  \begin{itemize}
  \item Correlate domain overlap behavior to linear system properties
  \item Analyze random walk transport with respect to the operator:
    \begin{itemize}
    \item Eigenvalues
    \item Sparsity
    \item Asymmetry
    \end{itemize}
  \item Evaluate communication cost
  \item Evaluate memory cost
  \end{itemize}

  \pause
  \textbf{Domain Replication Studies for Parallel Neumann-Ulam Method}
  \begin{itemize}
  \item Feasibility from a memory perspective
  \item Impact on scalability
  \item Impact on load balancing
  \end{itemize}

@@

  \textbf{Parallel Performance and Numerical Accuracy Studies for MCSA
    Method}
  \begin{itemize}
  \item Characterize Neumann-Ulam parameters required for good
    correction
  \item Feasibility of MCSA with full-clip Neumann-Ulam
  \item Performance for asymmetric systems
  \item Memory usage compared to Krylov methods
  \end{itemize}

  \pause
  \textbf{Parallel Performance and Numerical Accuracy Studies for FANM
    Method}
  \begin{itemize}
  \item Feasibility for problems of interest
  \item Memory usage vs. Newton-Krylov methods
  \item Scalability vs. Newton-Krylov methods
  \end{itemize}
